### 2021-03-25 Chapter-2/Chapter-2.tex
Updates from Overleaf

\section{Detection and Mitigation}
While there are several existing work on side-channel leakage detections, we find it very hard to apply existing methods to identify controlled-channel attacks. According to Table~\ref{table:side_channel_detection_tool}, existing methods can be classified into two categories, tools based on the trace comparison and tools based on the abstraction.

@@

\begin{tabular}{lllcclc}
\toprule
Tool & S/D & Method  & AVX/SIMD  & Multiple & Evaluation & Available \\ \midrule
CacheAudit~\cite{182946} & Static  & Abstraction  & \xmark & \xmark & Crypto Algorithm  & \cmark \\ 
CacheD~\cite{203878} & Dynamic  & Symbolic Execution + Taint Analysis  & \xmark & \xmark & Libgcrypt, OpenSSL & \xmark \\
CachSym~\cite{Brotzman19Casym} & Static & Symbolic Execution  & \xmark & \xmark & Crypto Snippet & \xmark \\
CacheS~\cite{236338} & Static & Abstract Interpretation & \xmark & \xmark & Libgcrypt, OpenSSL, mbedTLS & \xmark \\
DATA~\cite{217537} & Dynamic & Trace Alignment + Comparison & \cmark & \xmark & OpenSSL, PyCrypto & \cmark \\
ctgrind~\cite{langley2010ctgrind} & Dynamic & Taint Analysis & \cmark & \xmark & Crypto Library & \cmark \\
Satcco~\cite{xiao2017stacco} & Dynamic & Trace Comparison & \cmark & \xmark & OpenSSL, GnuTLS, mbedTLS, WolfTLS, LibreSSL & \xmark \\
ANABLEPS~\cite{wang2019time} & Dynamic & Trace Comparison & \cmark & \xmark & gsl, Hunspell, PNG, Freetype, QRcodegen, Genometools & \xmark \\
MicroWalk~\cite{wichelmann2018microwalk} & Dynamic & Trace Comparison & \cmark & \xmark & Intel IPP, Microsoft CNG & \cmark \\ 
\bottomrule
\end{tabular}
}
%\end{table*}
\end{sidewaystable}
Both hardware~\cite{Page2005PartitionedCA,
Wang:2007:NCD:1250662.1250723,Zhang:2015:HDL:2775054.2694372,Li:2014:SLH:2541940.2541947,
236344, 236334} and software~\cite{shih2017t,Coppens:2009:PMT:1607723.1608124,
brickell2006software,crane2015thwarting, 197207} side-channels mitigation techniques have
been proposed recently. Hardware countermeasures, including partitioning hardware resources~\cite{Page2005PartitionedCA}, randomizing cache
accesses~\cite{Wang:2007:NCD:1250662.1250723, 236344}, and designing new
architecture~\cite{tiwari2011crafting}, require changes to complex processors and are complex to adopt. On the contrary, software approaches are
usually easy to implement. Coppens et
al.~\cite{Coppens:2009:PMT:1607723.1608124} uses a compiler
to eliminate key-dependent control-flow transfers. Crane et
al.~\cite{crane2015thwarting} mitigated side-channels by randomizing software.
As for crypto libraries, the basic idea is to eliminate key-dependent
control-flow transfers and data accesses. Common approaches include
bit-slicing~\cite{konighofer2008fast,rebeiro2006bitslice} and unifying
control-flows~\cite{Coppens:2009:PMT:1607723.1608124}.

>>>>

\section{Detection and Mitigation}
There are several existing work on side-channel leakage detections. According to Table~\ref{table:side_channel_detection_tool}, existing methods can be classified into two categories, tools based on the trace comparison and tools based on the abstraction.

@@

\begin{tabular}{lllcclc}
\toprule
Tool & S/D & Method  & AVX/SIMD  & Multiple & Evaluation & Available \\ \midrule
CacheAudit~\cite{182946} & Static  & Abstraction  & \xmark & \xmark & Crypto Algorithm  & \cmark \\ 
CacheD~\cite{203878} & Dynamic  & Symbolic Execution + Taint Analysis  & \xmark & \xmark & Libgcrypt, OpenSSL & \xmark \\
CachSym~\cite{Brotzman19Casym} & Static & Symbolic Execution  & \xmark & \xmark & Crypto Snippet & \xmark \\
CacheS~\cite{236338} & Static & Abstract Interpretation & \xmark & \xmark & Libgcrypt, OpenSSL, mbedTLS & \xmark \\
DATA~\cite{217537} & Dynamic & Trace Alignment + Comparison & \cmark & \xmark & OpenSSL, PyCrypto & \cmark \\
ctgrind~\cite{langley2010ctgrind} & Dynamic & Taint Analysis & \cmark & \xmark & Crypto Library & \cmark \\
Satcco~\cite{xiao2017stacco} & Dynamic & Trace Comparison & \cmark & \xmark & OpenSSL, GnuTLS, mbedTLS, WolfTLS, LibreSSL & \xmark \\
ANABLEPS~\cite{wang2019time} & Dynamic & Trace Comparison & \cmark & \xmark & gsl, Hunspell, PNG, Freetype, QRcodegen, Genometools & \xmark \\
MicroWalk~\cite{Wichelmann:2018:MFF:3274694.3274741} & Dynamic & Trace Comparison & \cmark & \xmark & Intel IPP, Microsoft CNG & \cmark \\ 
\bottomrule
\end{tabular}
}
%\end{table*}
\end{sidewaystable}
Both hardware~\cite{Page2005PartitionedCA,
Wang:2007:NCD:1250662.1250723,Zhang:2015:HDL:2775054.2694372,Li:2014:SLH:2541940.2541947,
236344, 236334} and software~\cite{shih2017t,Coppens:2009:PMT:1607723.1608124,
brickell2006software,crane2015thwarting, 197207} side-channels mitigation techniques have
been proposed recently. Hardware countermeasures, including partitioning hardware resources~\cite{Page2005PartitionedCA}, randomizing cache
accesses~\cite{Wang:2007:NCD:1250662.1250723, 236344}, and designing new
architecture~\cite{tiwari2011crafting}, require changes to complex processors and are complex to adopt. On the contrary, software approaches are
usually easy to implement. Coppens et
al.~\cite{Coppens:2009:PMT:1607723.1608124} uses a compiler
to eliminate key-dependent control-flow transfers. Crane et
al.~\cite{crane2015thwarting} mitigated side-channels by randomizing software.
As for crypto libraries, the basic idea is to eliminate key-dependent
control-flow transfers and data accesses. Common approaches include
bit-slicing~\cite{konighofer2008fast,rebeiro2006bitslice} and unifying
control-flows~\cite{Coppens:2009:PMT:1607723.1608124}.
